Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation

### 2024-07-10 paper/appendix/bayes.tex
Ed: some typos, reference tidying, a bit more cosmetics
Updates from Overleaf

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth/\real{1.1}]{imgs/pmcmc/nuts.png}
    \caption{Convergence diagnostics for a No-U-Turn Sampler (NUTS) with uniform priors on a compact set. Again, we display the results for the trend parameter in the Dhaka cholera model of \cite{king08}. The NUTS sampler explores more of the posterior than the Metropolis-Hastings sampler, but fails to converge quickly.}
    \label{fig:nuts}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Recovery Rate.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Death Rate.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Reciprocal of Mean Immunity Duration.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Trend in Force of Infection.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Noise in Force of Infection.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Measurement Noise.png}
    \caption{Posterior estimates from NUTS powered by MOP-$\alpha$ with the informative nonparametric empirical prior obtained from a kernel density estimator on the IF2 parameter cloud. The posterior estimates from each chain are largely in agreement.}
    \label{fig:posteriors}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth/\real{1.25}]{imgs/pmcmc/nuts.png}
    \caption{Convergence diagnostics for a No-U-Turn Sampler (NUTS) with uniform priors on a compact set. Again, we display the results for the trend parameter in the Dhaka cholera model of \cite{king08}. The NUTS sampler explores more of the posterior than the Metropolis-Hastings sampler, but fails to converge quickly.}
    \label{fig:nuts}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Recovery_Rate.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Death_Rate.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Reciprocal_of_Mean_Immunity_Duration.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Trend_in_Force_of_Infection.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Noise_in_Force_of_Infection.png}
    \includegraphics[scale=0.33]{imgs/pmcmc/nuts_eb/Measurement_Noise.png}
    \caption{Posterior estimates from NUTS powered by MOP-$\alpha$ with the informative nonparametric empirical prior obtained from a kernel density estimator on the IF2 parameter cloud. The posterior estimates from each chain are largely in agreement.}
    \label{fig:posteriors}
\end{figure}
